Implicit yaddayadda

### 2011-09-27 papers/PLDI2012/implicitization.tex
Full path in \input{}.
The Makefile doesn't find the dependancy otherwise
typos and rewording

Guided static analysis \cite{DBLP:conf/sas/GopanR07} applies to the transition
graph of the program. One could instead apply the same technique to the implicit
multigraph from \cite{Monniaux_Gonnord_SAS11}, thus avoiding control flow merges with
unfeasible paths.
In this section, we use the same notations as \ref{sec:path_focusing}.

@@

We distinguish two phases when analysing a point $p_i \in P_R$:
\begin{enumerate}
\item We search for paths starting at point $p_i$, such that these paths are in
$P$, i.e are included in the working subgraph. Each time we find a path, we
update the abstract value of the destination point of the path. This is the
phase explained in \ref{subsec:ascending}.
\item  When the previous phase terminates, there is no more paths in
$P$, starting at $p_i$, 
that make the abstract values of the successors grow (otherwise, the SMT
solver would not have answered ``\emph{unsat}''). However, there may
exist such paths in the entire multigraph, that are not in $P$. The second phase
computes these paths and adds them to $P'$. We also use SMT solving to discover
these new paths, but we slightly change the SMT formula given to the SMT solver.
We now simply check for the satisfiability of $f(p_i)$ instead of $f(p_i) \wedge
P$. Since we already know that $f(p_i) \wedge P$ is \emph{unsatisfiable}, all
the paths given by the SMT solver won't be in $P$.
\end{enumerate}

@@

\begin{algorithm}
	\caption{ComputeNewPaths}
	\label{algo:computepaths}
	\begin{algorithmic}[1] 
	\input{algo/compute-paths}
	\end{algorithmic}
\end{algorithm}

@@

\begin{algorithm}
	\caption{Guided static analysis on implicit multigraph}
	\label{algo:combined}
	\begin{algorithmic}[1] 
	\input{algo/algo-combined}
	\end{algorithmic}
\end{algorithm}

Termination of this algorihm is guaranteed, because:
\begin{itemize}
\item 
the subset of paths $P$ is
strictly increasing at each loop iteration, and bounded by the finite set of
paths in the entire graph. 
\item the set $P'$ always verifies $P \cap P' = \emptyset$ by construction, 
which guarantees that $P$
will eventually be empty after a finite number of loop iterations.
\end{itemize}

@@

We choose $P_R$ as the set of loop headers of the function, plus the initial
state. In this case, we have three elements in $P_R$.
We also unroll the loop once, in order to distinguish the paths that don't go
through the loop from the others:
\begin{lstlisting}[numbers=none]
if (wait) {
   while (wait()) {}
}
\end{lstlisting}

>>>>

Guided static analysis \cite{DBLP:conf/sas/GopanR07} applies to the transition
graph of the program. We now present a new technique applying this analysis on the implicit
multigraph from \cite{Monniaux_Gonnord_SAS11}, thus avoiding control flow merges with
unfeasible paths.
In this section, we use the same notations as \ref{sec:path_focusing}.

@@

We distinguish two phases when analysing a point $p_i \in P_R$:
\begin{enumerate}
\item We search for paths starting at point $p_i$, such that these paths are in
$P$, i.e are included in the working subgraph. Each time we find a path, we
update the abstract value of the destination point of the path. This is the
phase explained in \ref{subsec:ascending}.
\item  When the previous phase terminates, there is no more paths in
$P$, starting at $p_i$, 
that make the abstract values of the successors grow (otherwise, the SMT
solver would not have answered ``\emph{unsat}''). However, there may
exist such paths in the entire multigraph, that are not in $P$. The second phase
computes these paths and adds them to $P'$. We also use SMT solving to discover
these new paths, but we slightly change the SMT formula given to the SMT solver:
we now simply check for the satisfiability of $f(p_i)$ instead of $f(p_i) \wedge
P$. Since we already know that $f(p_i) \wedge P$ is \emph{unsatisfiable}, all
the paths given by the SMT solver won't be in $P$.
\end{enumerate}

@@

\begin{algorithm}
	\caption{ComputeNewPaths}
	\label{algo:computepaths}
	\begin{algorithmic}[1] 
	\input{algo/compute-paths.tex}
	\end{algorithmic}
\end{algorithm}

@@

\begin{algorithm}
	\caption{Guided static analysis on implicit multigraph}
	\label{algo:combined}
	\begin{algorithmic}[1] 
	\input{algo/algo-combined.tex}
	\end{algorithmic}
\end{algorithm}

Termination of this algorihm is guaranteed, because:
\begin{itemize}
\item 
the subset of paths $P$ is
strictly increasing at each loop iteration, and bounded by the finite set of
paths in the entire graph. 
\item the set $P'$ always verifies $P \cap P' = \emptyset$ by construction, 
which guarantees that $P'$
will eventually be empty after a finite number of loop iterations.
\end{itemize}

@@

We choose $P_R$ as the set of loop headers of the function, plus the initial
state. In this case, we have three elements in $P_R$.
We also unroll the loop once, in order to distinguish the paths that do not go
through the loop from the others:
\begin{lstlisting}[numbers=none]
if (wait) {
   while (wait()) {}
}
\end{lstlisting}
